---
title: "vanderHoop_Animove"
author: "Julie van der Hoop"
date: "August 23, 2017"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Animove Notes - Aug 27 - 9 Sept  2017
Here are all the packages to install: 
install.packages(c("moveVis","pbs","dplyr","RStoolbox","move","ggmap","TwoStepCLogit","pbs","dplyr",'lubridate","fdrtool","circular","CircStats"),dependencies = T)

# Lecture Notes - Kami 28 Aug 2017
Lagrangian versus Eulerian methods: moving versus static. 
Lagrangian observe moving entity; eulerian observe space. 
Movement: Sequence of Location in time

Example data sets: Bat radio tracking data, African buffalo GPS data, "Leo" the vulture, "Leroy" and "Ricky" the fishers from Albany. --> all on movebank.org and data associated with R library move. 

This is a test

## Loading Datasets
```{r cars}
library("move")
# setwd("...")
# Bats <- move(...)

```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
