---
title: "vanderHoop_Animove"
author: "Julie van der Hoop"
date: "August 23, 2017"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Animove Notes - Aug 27 - 9 Sept  2017
Here are all the packages to install: 
install.packages(c("moveVis","pbs","dplyr","RStoolbox","move","ggmap","TwoStepCLogit","pbs","dplyr",'lubridate","fdrtool","circular","CircStats"),dependencies = T)

# Exercise to import our own data 28 Aug 2017
Import sperm whale files over a loop. Import .mat files, convert to R data frame, correct timestamp from MATLAB to R. 

## Loading Data
```{r}
library("move")
library('R.matlab')
setwd("/Users/julievanderhoop/Documents/R/Animove/Animove/")

mymoveobjects<-list()
# dtagfile <- readMat('./data/sw17_193atrk.mat')
mymoveobjects<-list()
# dtagfile <- readMat('./data/sw17_193atrk.mat')
myfilenames<-c("sw17_193a","sw17_196a","sw17_204a","sw17_225a")
for(i in myfilenames){
dtagfile <- readMat(paste('./data/',i,'trk.mat',sep=''))
# convert into a data frame
dtagfile$timestamp <- as.POSIXct((dtagfile$t - 719529)*86400, origin = "1970-01-01 00:00:00", tz = "UTC",format ="%Y-%m-%d %H:%M:%S")
dtagfile1 <- as.data.frame(dtagfile)
# convert MATLAB time time
dtagimport <- move(x=dtagfile1$lon,y=dtagfile1$lat,
                  time=dtagfile1$timestamp,
                  data=dtagfile1,proj=CRS("+proj=longlat"),
                  animal="sw17_193a", sensor="gps")

mymoveobjects[[i]]<-dtagimport
}
```

## Stack move objects
```{r}
mymovestack <- moveStack(mymoveobjects, forceTz="UTC")
```
## Plotting the data

Regular plot 

```{r}
plot(mymovestack)
```

ggmap plot
```{r}
map<-get_map(bbox(extent(mymovestack)*2), source='google')
dataDf<-as.data.frame(mymovestack)
ggmap(map)+
  geom_path(data=dataDf, aes(x=coords.x1, y=coords.x2))+
  xlab('Longitude')+ylab('Latitude')
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
